Microxanox - an R package for simulating an \(MICR\)obial ecosystem that can occupy \(OX\)ic or \(ANOX\)ic states.

### 2022-04-13 inst/manuscript/manuscript_microxanox.Rmd
Re-ordered for the format of SoftwareX

#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: 
  rticles::elsevier_article:
    includes: 
      in_header: headers.tex

@@

```{r setup, include = FALSE}
```

@@

| **Nr.** | **Code metadata description** | **Please fill in this column** |
|---|---|---|
| C1 | Current code version | v0.9.0 |
| C2 | Permanent link to code/repository used for this code version | [https://github.com/UZH-PEG/microxanox](https://github.com/UZH-PEG/microxanox) |
| C3 | Code Ocean compute capsule |  |
| C4 | Legal Code License   | CC BY 4.0 |
| C5 | Code versioning system used |git |
| C6 | Software code languages, tools, and services used | R | 
| C7 | Compilation requirements, operating environments | R (>= 4.1.0), ADD PACKAGES | 
| C8 | If available Link to developer documentation/manual |  |
| C9 | Support email for questions | Rainer.Krug@uzh.ch; Rainer@krugs.de |

@@

## General usability and flexibility of the model
The package is not intended to provide a modelling framework which can be adjusted easily to all needs, but primarily a tool to implement the model used by [@Bush2017] and to extend it to our needs [@REF_NEEDED]. Consequently, any more substantial changes and adaptaitions, are likely to need a change in the source code.

@@

# Software description
Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.

## Software Architecture
Give a short overview of the overall software architecture; provide a pic- torial component overview or similar (if possible). If necessary provide im- plementation details.

## Software Functionalities
Present the major functionalities of the software.

# Illustrative Examples
Provide at least one illustrative example to demonstrate the major functions.
Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel.

# Impact
This is the main section of the article and the reviewers weight the description here appropriately
Indicate in what way new research questions can be pursued as a result of the software (if any).
Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
Indicate in what way the software has changed the daily practice of its users (if so).
Indicate how widespread the use of the software is within and outside the intended user group.
Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).

# THIS NEEDS TO BE TRANSFERED IN THE FORMAT ABOVE

# The Model

The model is an implementation of the model described by [@Bush2017]. It is an ordinary differential equation (ODE) based numerical non-stochastic model which was implemented in form of an R package.

We use the notation from the [Table S1](LINK NEEDED) of the Supplementary information of [@Bush2017]), and not the notation in the main manuscript of [@Bush2017]. In the main manuscript the notation is simplified to `y_S_PB` ($y_{S,PB}$) (which is `y_SR_PB` ($y_{SR,PB}$) in Table S1) and `y_S_SB` ($y_{S,SB}$) (which is y_SO_SB ($y_{SO,SB}$) in Table S1). We also use `Pr_cB` ($Pr_B$) instead of `P_CB` ($P_{CB}$).

All parameter and variables follow these base dimensions:

- Time: `hours`
- Volume: `litres`
- Substrate quantity: `micromoles`
- Organism quantity: `cells`

<span style="color:red">{>> Add a more detailed description of the model and the additions <<}
{>>TODO<<}</span>

The ODEs are solved using the "General Solver for Ordinary Differential Equations" of the `deSolve` package [@Soetaert2010].

# Availability and Accessability of the package

The package is available in a [github repo/](https://github.com/UZH-PEG/microxanox/). The newest version is also available under the [DOI](https://DOI) or via RUniverse [@REF_NEEDED]. This manuscript describes version 1.0 which is available under [DOI](https://DOI) or installable within R by using `remotes::install_github("UZH-PEG", ref = "v1.0")`.

The package will be updated based on further research activities. It will be tested continuously for the last recent, current and devel version of R. 
<span style="color:green">{>>If we want that, we have to include some, even rudimentary, GITHUB tests.<<}
{>>RMK: Agreed - let's discuss this when we talk about the package paper.<<}
</span>

Issues, questions and suggestions should be communicated through the issue tracker at [https://github.com/UZH-PEG/microxanox/issues](https://github.com/UZH-PEG/microxanox/issues)

# Package description

## Documentation

The package contains the full documentetion of the functions, which includes

1. Standard R help for each function (`?COMMAND` in R)
2. Two vignettes acompanying the package:
  - A **User Guide**, also available on the R-Universe [Vignette 1](@LINK_NEEDED). This gives an introduction of the package and its functions and provides a walk-through of the process of running, visualizing and extra
   and [Vignette 2](@LINK_NEEDED)
3. This paper as a third vignette, also available under RUniverse [Vignette 3](@LINK_NEEDED)

## Reproducibility

@@

## Run the simulation and save the result
result <- run_simulatrion(parameter)
saveRDS(result, "sim1.rds")

@@

## Load results, change some parameter, and rerun the simulation and save the result
parameter <- loadRDS("sim1.rds")
# change some parameter
result <- run_simulatrion(parameter)
saveRDS(result, "sim2,rds")
```

## Using the package {#runsim}

We will now discuss the general structure and functiuonality of the package without going into to much detail. A more detailed discussion can be found in the [User Guide](LINK_NEEDED).

@@

In the following sections we describe the general usage of the package: running one simulation, finding steady states across an environmental gradient, calculating measures of stability, and visualisation.

@@

## Extracting Stability Measures
From the raw results returned by these `run_...()` functions, the stability measures can be extracted by using the function `get_stability_measures()`. These measures include non-linearity and hysteresis measures, of the response of the simulated system to environmental change.

# Use cases

@@

# Conclusions

{>>Dependant on journal<<}

>>>>

linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
output:
  rticles::elsevier_article:
    includes:
      in_header: headers.tex

@@

```{r setup, include = FALSE}
library(plantuml)
```

@@

| **Nr.** | **Code metadata description**                                | **Please fill in this column**                                                 |
|:-------:|:-------------------------------------------------------------|:-------------------------------------------------------------------------------|
| C1      | Current code version                                         | v0.9.0                                                                         |
| C2      | Permanent link to code/repository used for this code version | [https://github.com/UZH-PEG/microxanox](https://github.com/UZH-PEG/microxanox) |
| C3      | Code Ocean compute capsule                                   |                                                                                |
| C4      | Legal Code License                                           | CC BY 4.0                                                                      |
| C5      | Code versioning system used                                  | git                                                                            |
| C6      | Software code languages, tools, and services used            | R                                                                              |
| C7      | Compilation requirements, operating environments             | R (>= 4.1.0), ADD PACKAGES                                                     |
| C8      | If available Link to developer documentation/manual          |                                                                                |
| C9      | Support email for questions                                  | Rainer.Krug@uzh.ch; Rainer@krugs.de                                            |

@@

# Software description
{>>Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.<<}

```{plantuml runsim_example, eval = TRUE, plantuml.format = "auto", plantuml.preview = TRUE}
@startuml
partition "Run Single Simulation" {
   start
  :parameter <- new_runsim_parameter();
  split
    #palegreen:saveRDS(FILE, parameter);
    detach
  split again
    #pink:result <- run_simulation(parameter);
  end split
  split
    #palegreen:saveRDS(FILE, results);
    detach
  split again
    :Change some parameter;
    #pink:result2 <- run_simulation(results);
  end split
  split
    #palegreen:saveRDS(FILE, results2);
    detach
  split again
    end
  end split
}
@enduml
```

The package is not intended to provide a modelling framework which can be adjusted easily to all needs, but primarily a tool to implement the model used by [@Bush2017] and to extend it to our needs [@REF_NEEDED]. Consequently, any more substantial changes and adaptaitions, are likely to need a change in the source code.

@@

## Software Architecture
{>>Give a short overview of the overall software architecture; provide a pic- torial component overview or similar (if possible). If necessary provide im- plementation details.<<}

@@

## Run the simulation and save the result
result <- run_simulation(parameter)
saveRDS(result, "sim1.rds")

@@

## Load results, change some parameter, and rerun the simulation and save the result
parameter <- loadRDS("sim1.rds")
# change some parameter
result <- run_simulation(parameter)
saveRDS(result, "sim2,rds")
```

## Software Functionalities
{>>Present the major functionalities of the software.<<}

We will now discuss the general structure and functionality of the package without going into to much detail. A more detailed discussion can be found in the [User Guide](LINK_NEEDED).

@@

In the following sections we describe the general usage of the package: running one simulation, finding steady states across an environmental gradient, calculating measures of stability, and visualization.

# Illustrative Examples
{>>Present the major functionalities of the software.<<}

@@

### Extracting Stability Measures
From the raw results returned by these `run_...()` functions, the stability measures can be extracted by using the function `get_stability_measures()`. These measures include non-linearity and hysteresis measures, of the response of the simulated system to environmental change.

# Impact
{>>This is the main section of the article and the reviewers weight the description here appropriately
Indicate in what way new research questions can be pursued as a result of the software (if any).
Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
Indicate in what way the software has changed the daily practice of its users (if so).
Indicate how widespread the use of the software is within and outside the intended user group.
Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).<<}

@@

### 2022-04-13 inst/manuscript/manuscript_microxanox.tex
Re-ordered for the format of SoftwareX

\usepackage{lineno} % add

@@

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Microxanox - an R package for simulating an MICRobial ecosystem that can occupy OXic or ANOXic states.},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Nr.}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Code metadata description}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Please fill in this column}
\end{minipage} \\
\midrule
\endhead
C1 & Current code version & For example v42 \\
C2 & Permanent link to code/repository used for this code version &
\url{https://github.com/UZH-PEG/microxanox} \\
C3 & Code Ocean compute capsule & \\
C4 & Legal Code License & CC BY 4.0 \\
C5 & Code versioning system used & git \\
C6 & Software code languages, tools, and services used & R \\
C7 & Compilation requirements, operating environments & R (\textgreater=
4.1.0), ADD PACKAGES \\
C8 & If available Link to developer documentation/manual & \\
C9 & Support email for questions & Rainer.Krug@uzh.ch;
Rainer@krugs.de \\
\bottomrule
\end{longtable}

@@

Introduce the scientific background and the motivation for developing
the software. Explain why the software is important, and describe the
exact (scientific) problem(s) it solves. Indicate in what way the
software has contributed (or how it will con- tribute in the future) to
the process of scientific discovery; if available, this is to be
supported by citing a research paper using the software. Provide a
description of the experimental setting (how does the user use the
software?). Introduce related work in literature (cite or list
algorithms used, other software etc.).

Describe the software in as much as is necessary to establish a
vocabulary needed to explain its impact.

Give a short overview of the overall software architecture; provide a
pic- torial component overview or similar (if possible). If necessary
provide im- plementation details.

Present the major functionalities of the software.

Provide at least one illustrative example to demonstrate the major
functions. Optional: you may include one explanatory video that will
appear next to your article, in the right hand side panel.

This is the main section of the article and the reviewers weight the
description here appropriately Indicate in what way new research
questions can be pursued as a result of the software (if any). Indicate
in what way, and to what extent, the pursuit of existing research
questions is improved (if so). Indicate in what way the software has
changed the daily practice of its users (if so). Indicate how widespread
the use of the software is within and outside the intended user group.
Indicate in what way the software is used in commercial settings and/or
how it led to the creation of spin-off companies (if so).

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

{\{\textgreater\textgreater Biological justification and background -
one paragraph - DONE\textless\textless\} }

@@

\hypertarget{general-usability-and-flexibility-of-the-model}{%
\subsection{General usability and flexibility of the
model}\label{general-usability-and-flexibility-of-the-model}}

@@

\hypertarget{the-model}{%
\section{The Model}\label{the-model}}

The model is an implementation of the model described by
(\protect\hyperlink{ref-Bush2017}{Bush et al., 2017}). It is an ordinary
differential equation (ODE) based numerical non-stochastic model which
was implemented in form of an R package.

We use the notation from the \href{LINK\%20NEEDED}{Table S1} of the
Supplementary information of (\protect\hyperlink{ref-Bush2017}{Bush et
al., 2017})), and not the notation in the main manuscript of
(\protect\hyperlink{ref-Bush2017}{Bush et al., 2017}). In the main
manuscript the notation is simplified to \texttt{y\_S\_PB}
(\(y_{S,PB}\)) (which is \texttt{y\_SR\_PB} (\(y_{SR,PB}\)) in Table S1)
and \texttt{y\_S\_SB} (\(y_{S,SB}\)) (which is y\_SO\_SB (\(y_{SO,SB}\))
in Table S1). We also use \texttt{Pr\_cB} (\(Pr_B\)) instead of
\texttt{P\_CB} (\(P_{CB}\)).

All parameter and variables follow these base dimensions:

\begin{itemize}
\tightlist
\item
  Time: \texttt{hours}
\item
  Volume: \texttt{litres}
\item
  Substrate quantity: \texttt{micromoles}
\item
  Organism quantity: \texttt{cells}
\end{itemize}

{\{\textgreater\textgreater{} Add a more detailed description of the
model and the additions \textless\textless\}
\{\textgreater\textgreater TODO\textless\textless\}}

The ODEs are solved using the ``General Solver for Ordinary Differential
Equations'' of the \texttt{deSolve} package
(\protect\hyperlink{ref-Soetaert2010}{Soetaert et al., 2010}).

\hypertarget{availability-and-accessability-of-the-package}{%
\section{Availability and Accessability of the
package}\label{availability-and-accessability-of-the-package}}

The package is available in a
\href{https://github.com/UZH-PEG/microxanox/}{github repo/}. The newest
version is also available under the \href{https://DOI}{DOI} or via
RUniverse (\protect\hyperlink{ref-REF_NEEDED}{REF NEEDED, 2222}). This
manuscript describes version 1.0 which is available under
\href{https://DOI}{DOI} or installable within R by using
\texttt{remotes::install\_github("UZH-PEG",\ ref\ =\ "v1.0")}.

The package will be updated based on further research activities. It
will be tested continuously for the last recent, current and devel
version of R. {\{\textgreater\textgreater If we want that, we have to
include some, even rudimentary, GITHUB tests.\textless\textless\}
\{\textgreater\textgreater RMK: Agreed - let's discuss this when we talk
about the package paper.\textless\textless\} }

Issues, questions and suggestions should be communicated through the
issue tracker at \url{https://github.com/UZH-PEG/microxanox/issues}

\hypertarget{package-description}{%
\section{Package description}\label{package-description}}

\hypertarget{documentation}{%
\subsection{Documentation}\label{documentation}}

The package contains the full documentetion of the functions, which
includes

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Standard R help for each function (\texttt{?COMMAND} in R)
\item
  Two vignettes acompanying the package:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  A \textbf{User Guide}, also available on the R-Universe
  \href{@LINK_NEEDED}{Vignette 1}. This gives an introduction of the
  package and its functions and provides a walk-through of the process
  of running, visualizing and extra and \href{@LINK_NEEDED}{Vignette 2}
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  This paper as a third vignette, also available under RUniverse
  \href{@LINK_NEEDED}{Vignette 3}
\end{enumerate}

\hypertarget{reproducibility}{%
\subsection{Reproducibility}\label{reproducibility}}

@@

\DocumentationTok{\#\# Run the simulation and save the result}
\NormalTok{result }\OtherTok{\textless{}{-}} \FunctionTok{run\_simulatrion}\NormalTok{(parameter)}
\FunctionTok{saveRDS}\NormalTok{(result, }\StringTok{"sim1.rds"}\NormalTok{)}

@@

\DocumentationTok{\#\# Load results, change some parameter, and rerun the simulation and save the result}
\NormalTok{parameter }\OtherTok{\textless{}{-}} \FunctionTok{loadRDS}\NormalTok{(}\StringTok{"sim1.rds"}\NormalTok{)}
\CommentTok{\# change some parameter}
\NormalTok{result }\OtherTok{\textless{}{-}} \FunctionTok{run\_simulatrion}\NormalTok{(parameter)}
\FunctionTok{saveRDS}\NormalTok{(result, }\StringTok{"sim2,rds"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{runsim}{%
\subsection{Using the package}\label{runsim}}

We will now discuss the general structure and functiuonality of the
package without going into to much detail. A more detailed discussion
can be found in the \href{LINK_NEEDED}{User Guide}.

@@

In the following sections we describe the general usage of the package:
running one simulation, finding steady states across an environmental
gradient, calculating measures of stability, and visualisation.

@@

\hypertarget{extracting-stability-measures}{%
\subsection{Extracting Stability
Measures}\label{extracting-stability-measures}}

@@

\hypertarget{use-cases}{%
\section{Use cases}\label{use-cases}}

@@

{\{\textgreater\textgreater More details from the
paper.\textless\textless\}\\
\{\textgreater\textgreater Romana will provide two or three
sentences\textless\textless\}}

\hypertarget{conclusions-1}{%
\section{Conclusions}\label{conclusions-1}}

\{\textgreater\textgreater Dependant on journal\textless\textless\}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Soetaert2010}{}}%
Soetaert, K., Petzoldt, T., Setzer, R.W., 2010. Solving differential
equations in {R}: {Package deSolve}. Journal of Statistical Software 33,
1--25.
doi:\href{https://doi.org/10.18637/jss.v033.i09}{10.18637/jss.v033.i09}

>>>>

\usepackage{lineno} % add
  \linenumbers % turns line numbering on

@@

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Microxanox - an R package for simulating an MICRobial ecosystem that can occupy OXic or ANOXic states.},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0596}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4106}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.5298}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
\textbf{Nr.}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Code metadata description}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Please fill in this column}
\end{minipage} \\
\midrule
\endhead
C1 & Current code version & v0.9.0 \\
C2 & Permanent link to code/repository used for this code version &
\url{https://github.com/UZH-PEG/microxanox} \\
C3 & Code Ocean compute capsule & \\
C4 & Legal Code License & CC BY 4.0 \\
C5 & Code versioning system used & git \\
C6 & Software code languages, tools, and services used & R \\
C7 & Compilation requirements, operating environments & R (\textgreater=
4.1.0), ADD PACKAGES \\
C8 & If available Link to developer documentation/manual & \\
C9 & Support email for questions & Rainer.Krug@uzh.ch;
Rainer@krugs.de \\
\bottomrule
\end{longtable}

@@

@@

\{\textgreater\textgreater Describe the software in as much as is
necessary to establish a vocabulary needed to explain its
impact.\textless\textless\}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{@startuml}
\NormalTok{partition "Run Single Simulation" \{}
\NormalTok{   start}
\NormalTok{  :parameter \textless{}{-} new\_runsim\_parameter();}
\NormalTok{  split}
\NormalTok{    \#palegreen:saveRDS(FILE, parameter);}
\NormalTok{    detach}
\NormalTok{  split again}
\NormalTok{    \#pink:result \textless{}{-} run\_simulation(parameter);}
\NormalTok{  end split}
\NormalTok{  split}
\NormalTok{    \#palegreen:saveRDS(FILE, results);}
\NormalTok{    detach}
\NormalTok{  split again}
\NormalTok{    :Change some parameter;}
\NormalTok{    \#pink:result2 \textless{}{-} run\_simulation(results);}
\NormalTok{  end split}
\NormalTok{  split}
\NormalTok{    \#palegreen:saveRDS(FILE, results2);}
\NormalTok{    detach}
\NormalTok{  split again}
\NormalTok{    end}
\NormalTok{  end split}
\NormalTok{\}}
\NormalTok{@enduml}
\end{Highlighting}
\end{Shaded}

\includegraphics{/var/folders/50/wcr5bjwn75q595n6x82gxj280000gq/T//RtmpRw3cq4/runsim_example.pdf}

@@

\{\textgreater\textgreater Give a short overview of the overall software
architecture; provide a pic- torial component overview or similar (if
possible). If necessary provide im- plementation
details.\textless\textless\}

@@

\DocumentationTok{\#\# Run the simulation and save the result}
\NormalTok{result }\OtherTok{\textless{}{-}} \FunctionTok{run\_simulation}\NormalTok{(parameter)}
\FunctionTok{saveRDS}\NormalTok{(result, }\StringTok{"sim1.rds"}\NormalTok{)}

@@

\DocumentationTok{\#\# Load results, change some parameter, and rerun the simulation and save the result}
\NormalTok{parameter }\OtherTok{\textless{}{-}} \FunctionTok{loadRDS}\NormalTok{(}\StringTok{"sim1.rds"}\NormalTok{)}
\CommentTok{\# change some parameter}
\NormalTok{result }\OtherTok{\textless{}{-}} \FunctionTok{run\_simulation}\NormalTok{(parameter)}
\FunctionTok{saveRDS}\NormalTok{(result, }\StringTok{"sim2,rds"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\{\textgreater\textgreater Present the major functionalities of the
software.\textless\textless\}

We will now discuss the general structure and functionality of the
package without going into to much detail. A more detailed discussion
can be found in the \href{LINK_NEEDED}{User Guide}.

@@

In the following sections we describe the general usage of the package:
running one simulation, finding steady states across an environmental
gradient, calculating measures of stability, and visualization.

\{\textgreater\textgreater Present the major functionalities of the
software.\textless\textless\}

@@

\hypertarget{extracting-stability-measures}{%
\subsubsection{Extracting Stability
Measures}\label{extracting-stability-measures}}

@@

\{\textgreater\textgreater This is the main section of the article and
the reviewers weight the description here appropriately Indicate in what
way new research questions can be pursued as a result of the software
(if any). Indicate in what way, and to what extent, the pursuit of
existing research questions is improved (if so). Indicate in what way
the software has changed the daily practice of its users (if so).
Indicate how widespread the use of the software is within and outside
the intended user group. Indicate in what way the software is used in
commercial settings and/or how it led to the creation of spin-off
companies (if so).\textless\textless\}

@@

{\{\textgreater\textgreater More details from the
paper.\textless\textless\} \{\textgreater\textgreater Romana will
provide two or three sentences\textless\textless\}}

@@
